---
title: "Background Quality Report Template"
lang: "en"
output: 
  html_document:
    code_folding: none
    toc: true
    toc_float: true
    toc_depth: 4
    code_download: no
    css: "style.css"
    includes:
      in_header:
        - "meta.html"
        - "consent_head.html"
      after_body:
        - "cookie_banner.html"
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../outputs/",
      envir = globalenv()
    )
  })
params:
  annotations:
    true
---

<div id="cookie-banner"></div>

```{r settings, include=FALSE}
# This code sets the default options for all chunks in this file
knitr::opts_chunk$set(
  message = FALSE, warning = FALSE, echo = FALSE
)

if (!require(here)) install.packages("here")
library(here)

source(here("code/data_prep.R"))
```

<!-- This is the top banner. Add your publication name -->

<div data-nics-theme="`r nics_theme`">

<header>
`r f_banner(title = rmarkdown::metadata$title, subtitle = "insert publication name")`
</header>

<main>

<!-- This is the standard introduction used in every BQR. Add your publication
name and a link to your publication series page where indicated below -->

This report provides information on the quality of the data used to produce the
official statistics: [insert publication name](insert link to publication series page).
It informs users about the quality of the information upon which they may be
drawing conclusions and making decisions.

The report looks at five ways to measure statistical quality. These are based on
the [European Statistics Code of Practice, PDF (458 KB)](https://ec.europa.eu/eurostat/documents/4031688/8971242/KS-02-18-142-EN-N.pdf/e7f85f07-91db-4312-8118-f729c75878c7?t=1528447068000).
The [Code of Practice for Statistics](https://code.statisticsauthority.gov.uk/)
says that organisations that produce official statistics must:

> __6.10__ Verify that the statistics are representative and of suitable quality
and monitor relevant quality dimensions for both input data and the statistics,
such as completeness and validity, accuracy and reliability, coherence and
comparability, and timeliness. Quantify statistical error, including bias,
and produce measures of confidence, where possible.    
>
> __7.2__ Report on the key quality dimensions such as accuracy and timeliness,
and, where possible, give estimates of error and confidence for the statistics.
Summarise how uncertainty in the estimates may impact use by using qualifying
words, numbers or graphics.

<!-- The headers and bold text below must be included in your BQR, the other
sections must be replaced with your own text-->

##  Introduction

Things to consider:

- a brief history of the statistical process and output
- the method used to create the publication
- overview of the production and dissemination process
- documentation available, particularly relating to methodology and quality

##  Relevance

**Does the information meet people's needs?**
**This means checking whether statistics cover the right people, places and**
**topics.**

Things to consider:

- what statistics are included
- who or what the statistics are about
- clear explanations of any terms or definitions used
- whether the statistics meet relevant standards or guidelines
- any information users have asked for but is not available, and why
- any measures that show the quality of the statistics

##  Accuracy

**Accuracy means how close an estimate is to the real value.**

Things to consider:

- how the statistics were produced
- whether the methods follow recognised standards
- the main sources of error
- any bias that could affect the results

For surveys, include:

- sampling errors (using a sample instead of everyone)
- coverage errors (missing people or including the wrong people)
- measurement errors (incorrect answers or measurements)
- non-response errors (people not taking part)
- processing errors (mistakes when handling data)

For statistics based on administrative data, include:

- under-coverage and over-coverage
- errors in classification variables
- unreported events, where relevant

## Timeliness and punctuality

**Timeliness refers to the time gap between publication and the reference**
**period. Punctuality refers to the gap between planned and actual publication**
**dates.**

Things to consider:

- how long it takes to produce each release
- how often releases are published on time
- reasons why any releases were late

## Accessibility and clarity

**Accessibility means how easy it is to get and use the data.**
**Clarity means how easy the information is to understand.**

Things to consider:

- explain how people can access the data 
- include information that helps people understand the statistics
- show how the needs of different users have been met
- include feedback on how easy the statistics are to find and understand

## Coherence and comparability

**Coherence means checking whether information from different sources gives a**
**similar picture.**
**Comparability means checking whether information can be compared across**
**different time periods, places or groups.**

Things to consider:

- anything that could make the statistics harder to compare
- how much any differences affect the results
- any differences from UK, European or international standards
- whether the statistics can be compared over time
- whether the statistics can be compared across different places
- whether the statistics tell the same story within the dataset
- whether they agree with other related statistics

Geographies might be an important topic to include here:

- Explain if changes to boundaries or areas affect comparisons over time. 
- Explain if data collected in different areas can be compared fairly

Things users should know:

- explain any common mistakes people make when using the statistics
- explain how the statistics should be used and understood 
- signpost users to other statistics if they may be more suitable

## Balancing different needs

**People who produce statistics often have to make choices about where to get**
**their data from and how to collect it.**

For example, they may need to choose between using existing administrative data
or carrying out a new survey. A survey can ask exactly the right questions, but
it can take a lot of time and money. Administrative data may be cheaper and
available more quickly, but it might not include everything that is needed.

Things to include and consider:

- what data sources were chosen
- why these sources were chosen
- other options that were considered
- the advantages and disadvantages of each option
- how these choices affected the statistics
- any choices that may need to be reviewed in the future

## What do users need?

**This section looks at who uses the statistics, what they use them for, and**
**what they think about them.**

Things to include:

- how you find out who uses the statistics 
- the different groups of people who use them
- what people use the statistics for
- any users or uses that need special attention
- how you collect feedback from users
- what users say about the statistics
- when you last asked users for their feedback

## Performance, cost and respondent burden

**This looks at how well the statistics work, what they cost to produce, and**
**how much time they take from people who provide information.**

Things to include:

- the cost of producing the statistics each year
- how much time people spend providing information
- how staff time and resources are used
- how the cost compares with other statistical outputs, where useful

## Confidentiality, transparency and security

**This section explains how information is protected and how organisations are**
**open about how they produce statistics.**

Things to include:

- how information is kept private
- how information is kept safe
- how statistics are produced in an open and clear way
- the rules used to protect information
  
</main>

```{r render-footer, results='asis', echo=FALSE}
f_footer()
```

`r if (params$annotations) '<script src = "annotation.js"></script>'`

</div>

```{js}

// Function to add tabs to table of contents

function tabOrder() {

  // Make side menu tabbable

  let headings = document.getElementsByClassName(
    "tocify-item list-group-item"
  );

  let sections = document.getElementsByClassName(
    "section"
  );

  for (let i = 0; i < headings.length; i++) {
    headings[i].innerHTML =
      "<a href='#" +
      sections[i].id +
      "'>" +
      headings[i].innerHTML +
      "</a>";
  }
}

// Instruct web browser to run above function when loaded
window.onload = tabOrder;
```
